### 2019-11-05 tikz/config.tex
Review - figures are modified
Remove Useless Tikz setting

\definecolor{colorblack}{rgb}{0, 0, 0}
\definecolor{colorblue}{rgb}{0, 0.4470, 0.7410}
\definecolor{colorred}{rgb}{0.8500, 0.3250, 0.0980}
\definecolor{coloryellow}{rgb}{0.9290, 0.6940, 0.1250}
\definecolor{colorpurple}{rgb}{0.4940, 0.1840, 0.5560}
\definecolor{colorgreen}{rgb}{0.4660, 0.6740, 0.1880}
\definecolor{colorcyan}{rgb}{0.3010, 0.7450, 0.9330}
\definecolor{colorbordeau}{rgb}{0.6350, 0.0780, 0.1840}

% Main color
\definecolor{maincolor}{RGB}{89, 9, 38}
\definecolor{secondcolor}{RGB}{20, 9, 89}

@@

\pgfplotsset{upperbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=60}}]
\pgfplotsset{lowerbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=-60}}]

\pgfplotsset{
  /pgfplots/upperbound/.style 1 args={
    legend image code/.code={
      \draw[##1, upperbound]
        plot coordinates {
        (0cm,0cm)
        (0.6cm,0cm)
      }
    }
  }
}

@@

\newcommand{\AxisRotator}[1][rotate=0]{%
  \tikz [x=0.1cm,y=0.30cm,-stealth,#1] \draw (0,0) arc (-150:150:1 and 1);%
}

@@

>>>>

\definecolor{mycolor1}{RGB}{79,115,193}
\definecolor{mycolor2}{RGB}{213,91,53}
\definecolor{mycolor3}{RGB}{152,126,49}

@@

@@

@@

\tikzset{block/.default={0.8cm}{0.8cm}}
\tikzset{addb/.append style={scale=0.7}}
\tikzset{node distance=0.6}
